Check Coverage

### 2019-09-11 analysis/merge_data.Rmd
Code for picking up FD calculations where they leave off after crashing.

```{r}
library(tidyverse)
library(FD)
```

@@

fd_data <- biotime_traits %>% 
  filter(study_id == 56) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd(.x, study = .y$study_id, plot = .y$plot))
```

>>>>

```{r}
library(tidyverse)
library(FD)
devtools::load_all()
```

@@

fd <- biotime_traits %>% 
  filter(!is.na(plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
```

Read data back in:
```{r}
files <-  dir(here::here("data", "fd_output"), "*.tsv")

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)

fd <- biotime_traits %>% 
  filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
  anti_join(fd_data) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))

#4610981
#7611121

```
